Hierarchical Control for Aircraft Electronic Power Systems

### 2012-12-08 project/report/paper.tex
quick intro in the experimental results section

\section{Experimental Results}
\label{sec:results}
\begin{figure}[htb]
  \centering
  \includegraphics[width=\columnwidth]{figures/preqnofail}
  \caption{\textbf{Power Request}
  Historical data of power request on Bus 1 and Bus 2 for time 0
  to 100. Notice the spikes in power usage on Bus 2 that pulls the
  request over 100000 Watts, well over the power rating of the generators.
  Load shedding is a must during those intervals.}
  \label{fig:preqnofail}
\end{figure}

>>>>

\section{Experimental Results}
In this section, we simulate a number of system configurations that demonstrate the Hierarchical LMS's combination of safe operation and optimization where feasible.
The examples in Section~\ref{sec:numerical-examples} provide the intuition for some of these simulation experiments, and the simulations help to further validate the Hierarchical LMS.
Our simulation setup is constructed in Matlab and Simulink, and the Optimizing LMS uses CPLEX to solve its optimization problem.

\label{sec:results}
\begin{figure}[htb]
  \centering
  \includegraphics[width=\columnwidth]{figures/preqnofail}
  \caption{\textbf{Power Request}
  Historical data of power request on Bus 1 and Bus 2 for time 0
  to 100. Notice the spikes in power usage on Bus 2 that pulls the
  request over 100000 Watts, well over the power rating of the generators.
  Load shedding is a must during those intervals.}
  \label{fig:preqnofail}
\end{figure}
